Results

### 2018-03-21 02_analysis.Rmd
Specify better priors

```{r build-models-amount, warning=FALSE, message=FALSE, cache=TRUE}
# Basic interaction models
m_amount_c <- stan_glm(amount_donate ~ crackdown,
                       data = results, family = gaussian(),
                       prior = student_t(df = 1, location = 0),
                       prior_intercept = student_t(df = 1, location = 0),
                       chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)

@@

```{r build-models-likely, warning=FALSE, message=FALSE, cache=TRUE}
# Basic interaction models
# Weakly informative normal priors, since these coefficients are log-odds
m_likely_c <- stan_glm(donate_likely_bin ~ crackdown,
                       data = results, family = binomial(link = "logit"),
                       prior = normal(-1, 1),
                       prior_intercept = normal(-1, 1),
                       chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)

@@

```{r tbl-models-likely, results="asis"}
huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
       m_likely_c_full, m_likely_ci_full, m_likely_cif_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %>% 
  quick_docx()
  print_hux()
```

>>>>

```{r build-models-amount, warning=FALSE, message=FALSE, cache=TRUE}
# Basic interaction models
m_amount_c <- stan_glm(amount_donate ~ crackdown,
                       data = results, family = gaussian(),
                       prior = cauchy(location = 0, scale = 2.5),
                       prior_intercept = cauchy(location = 0, scale = 10),
                       chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)

@@

```{r build-models-likely, warning=FALSE, message=FALSE, cache=TRUE}
# Basic interaction models
# Weakly informative student t priors, since these coefficients are log-odds
# See https://github.com/stan-dev/stan/wiki/Prior-Choice-Recommendations#prior-for-the-regression-coefficients-in-logistic-regression-non-sparse-case and https://arxiv.org/abs/1507.07170
m_likely_c <- stan_glm(donate_likely_bin ~ crackdown,
                       data = results, family = binomial(link = "logit"),
                       prior = student_t(3, 0, 2.5),
                       prior_intercept = student_t(3, 0, 10),
                       chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)

@@

```{r tbl-models-likely, results="asis"}
huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
       m_likely_c_full, m_likely_ci_full, m_likely_cif_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %>% 
  print_hux()
```
